On the presentation of orthogonal groups over polynomial rings

### 2019-05-04 dl-paper.tex
Minor fix

@@

In fact, we could prove something a little bit stronger.
\begin{lemma}
 Let $g$ be an element of $K(A[X], M[X])$, then for any pair of roots $\alpha, \beta \in \Phi$, $\alpha \neq \pm \beta$
 the element $g$ can be written as a product $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $m, m' \in M$ and
  $g_0 \in K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0)$.

 The group $K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0)$ admits generating set consisting of the following elements:
 \begin{itemize}
  \item $z_\gamma(Xf, \xi)$, $\gamma \in \Phi \setminus\{ \pm \alpha, \pm \beta\};$
  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$, $z_{\alpha}(Xf, X\xi)$, $z_\beta(Xf, X\xi)$;
  \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi$, $\delta \not \in \{ \pm \alpha, \pm \beta \}$
 \end{itemize}
\end{lemma}
\begin{proof}
 %Follows from~\cref{Kgen-strong}, \cref{P0_normal} and Stepanov's theorem.
 Embed $\alpha$ and $\beta$ in some subsystem $\Psi$ of type $A_3$ and denote by $\Sigma$ the special part of the parabolic subset $S = \Psi \cup \Phi^+$.
 Applying~\cref{thm:Stepanov} to $S$ we obtain that every element of $\St(\Phi, A[X], XM[X])$ can be presented as a product of 
  $z_\gamma(Xf, \xi)$, $\gamma \in \Sigma(S) \subseteq \Phi^+\setminus \{ \pm \alpha, \pm \beta \}$ and $x_\gamma(Xf)$, $\gamma \in \{ \pm \alpha, \pm \beta \}$.

 The next step of the proof is to write each factor of the form $x_{\epsilon}(Xf)$, $\epsilon \in \{-\alpha,-\beta\}$ appearing in this product as
 $x_{\epsilon}(X^2f') \cdot x_{\epsilon}(mX)$ and then move $x_{\epsilon}(mX)$ to the rightmost position
  (conjugating by $x_{\epsilon}(mX)$ all factors along the way).
 Notice that no terms of the form $x_{\epsilon}(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ may appear after the simplification of conjugates.
 Indeed, notice that the extra terms in the right-hand sides of \eqref{eq3-1} and~\eqref{eq3-2} 
 (as well as all terms in the right-hand sides of~\eqref{C1},\eqref{C2} of~\cref{Crels} if you substitute proper values into it)
  have terms of degree at least $2$ in $X$. As a side effect of this operation, however, terms $x_\alpha(Xf)$ and $x_\beta(Xf)$ appearing in $g$ could have turned into
   $z_\alpha(Xf, X\xi)$, and $z_\beta(Xf, X\xi)$ for some $\xi \in A[X]$.
 After collecting terms of the form $x_\epsilon(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ in the right-hand side of the resulting expression
  we obtain the desired decomposition for $g$. \end{proof}

>>>>

In fact, we could prove something a little bit stronger.
\begin{lemma} \label{K-a-b}
 Let $g$ be an element of $K(A[X], M[X])$, then for any pair of roots $\alpha, \beta \in \Phi$, $\alpha \neq \pm \beta$
 the element $g$ can be written as a product $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $m, m' \in M$ and
  $g_0 \in K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0)$.

 The group $K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0)$ admits generating set consisting of the following elements:
 \begin{itemize}
  \item $z_\gamma(Xf, \xi)$, $\gamma \in \Phi \setminus\{ \pm \alpha, \pm \beta\};$
  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$, $z_{\alpha}(Xf, X\xi)$, $z_\beta(Xf, X\xi)$;
  \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi$, $\delta \not \in \{ \pm \alpha, \pm \beta \}$
 \end{itemize}
\end{lemma}
\begin{proof}

 Embed $\alpha$ and $\beta$ in some subsystem $\Psi$ of type $A_3$ and denote by $\Sigma$ the special part of the parabolic subset $S = \Psi \cup \Phi^+$.
 Applying~\cref{thm:Stepanov} to $S$ we obtain that every element of $\St(\Phi, A[X], XM[X])$ can be presented as a product of 
  $z_\gamma(Xf, \xi)$, $\gamma \in \Sigma(S) \subseteq \Phi^+\setminus \{ \pm \alpha, \pm \beta \}$ and $x_\gamma(Xf)$, $\gamma \in \{ \pm \alpha, \pm \beta \}$.

 The next step of the proof is to write each factor of the form $x_{\epsilon}(Xf)$, $\epsilon \in \{-\alpha,-\beta\}$ appearing in this product as
 $x_{\epsilon}(X^2f') \cdot x_{\epsilon}(mX)$ and then move $x_{\epsilon}(mX)$ to the rightmost position
  (conjugating by $x_{\epsilon}(mX)$ all factors along the way).
 Notice that no terms of the form $x_{\epsilon}(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ may appear after the simplification of conjugates,
  so this process is guaranteered to end.
 Indeed, notice that the extra terms in the right-hand sides of \eqref{eq3-1} and~\eqref{eq3-2} 
 (as well as all terms in the right-hand sides of~\eqref{C1},\eqref{C2} of~\cref{Crels} if you substitute proper values into it)
  have terms of degree at least $2$ in $X$. As a side effect of this operation, however, terms $x_\alpha(Xf)$ and $x_\beta(Xf)$ appearing in $g$ could have turned into
   $z_\alpha(Xf, X\xi)$, and $z_\beta(Xf, X\xi)$.
 After collecting terms of the form $x_\epsilon(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ in the right-hand side of the resulting expression
  we obtain the desired decomposition for $g$. \end{proof}

@@
